%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle[nosymbols]{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=.94]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.2cm}
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\usepackage{mathptmx}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\firstname{Zhongyuan} % Your first name
\familyname{Wang} % Your last name

% All information in this block is optional, comment out any lines you don't need


% \address{University College London, Gower Street, London, UK}

\email{wang1504626@gmail.com}

% \github{github.com/KevinDennyII} 

\extrainfo{
  \href{https://www.linkedin.com/in/zhongyuanwang}{linkedin.com/in/zhongyuanwang}
}


\begin{document}

\makecvtitle
\vspace{-2em}
\begin{center}
\textit{Founding ML Scientist specializing in Agentic AI, LLM systems, and ML. 20 patents. 5 enterprise customers across the US, India, and the Gulf.}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experiences}
\cventry{2024 -- Present}{Founding ML Scientist}{RaptorX.AI, Remote}{}{}{
\begin{itemize}
\item Built a production-style Agentic Engineering workflow for bank fraud alerts: Agent Loop, context management, planning, Guardrails, case-store state, Evidence/Report agents, SFT/RLVR/RLHF, evaluation, and runtime/MLOps
\item Built criteria-driven multi-agent systems for paper/patent production; as lead of a five-person ML team, owned technical direction, experiment checks, drafting, counsel handoff, and audit logs
\item Built the underlying unsupervised fraud engine from zero: GNNs, behavioral autoencoders, explainability, and a 30-type edge-probability model to reduce label dependency
\item Achieved 328$\times$ candidate reduction (590K $\rightarrow$ 1,883 high-confidence alerts), 99.9\% fraud-type specificity
\item Converted PoCs into 5 signed enterprise customers across the US, India, and the Gulf: Payactiv (US), NSDL and Lenskart (India), Omantel and Thawani Pay (Oman); US deployment covers 460K+ users across 6,700+ employers
\end{itemize}
}
\cventry{2021 -- 2024}{Senior Engineer, AI \& Data Platform for Autonomous Driving}{Lotus Tech (Geely Group), Hangzhou, China}{}{}
{
\begin{itemize}
\item Led an in-house video anonymization pipeline from vehicle data ingestion to data-center processing, supporting 80+ TB/day fleet-scale autonomous-driving data
\item Trained and deployed YOLOv5-based face/license-plate detection across 10M+ frames, achieving 90\%+ recall for privacy-sensitive objects
\item Built a Volcano-based Kubernetes GPU job scheduling platform for PyTorch workloads on a local 64-GPU NVIDIA A100 80GB cluster (8 nodes $\times$ 8 GPUs), improving utilization and saving $\sim$RMB 4M/year versus Alibaba Cloud
\item Optimized GPU-accelerated batch inference for fleet-scale video processing, reducing latency 30\% and improving throughput
\item Replaced third-party vendors with an internal ML platform, saving $\sim$\$1M/year while supporting GDPR/PIPL compliance
\end{itemize}
}
\cvitem{2020 -- 2021}{\textbf{Independent ML Study \& Graph-ML Projects}
\begin{itemize}
\item Self-directed study of graph machine learning: implemented GNN models for node classification and link prediction on public Kaggle datasets
\end{itemize}
}
\cventry{2020}{Software Development Engineer, Financial Anti-Fraud}{DataVisor, Shanghai, China}{}{}
{
\begin{itemize}
\item \textbf{Production Fraud Detection for Top-Tier Commercial Bank:}
  \begin{itemize}
    \item Built an unsupervised loan application fraud model combining GNN and traditional ML, using hundreds of features spanning behavioral, device, third-party credit, and raw transaction data
    \item Directly contributed to securing a \$500,000 enterprise contract through technical leadership and client demonstration
  \end{itemize}
\end{itemize}
}

\cventry{2019}{UCL-DiDi Master Research Program}{Intern, DiDi AI Labs, Beijing, China}{}{}
{
\textbf{Supervisor}: Prof. Jieping Ye (VP of DiDi Chuxing, IEEE Fellow). \\
\textbf{Project:} Leveraging Graph Neural Networks for User Travel Intent Prediction. \\
Selected as one of only 2 projects (out of 30+ candidates) across the entire UCL cohort for the DiDi AI Labs research program. \\
This work laid the foundation for applying GNNs to financial fraud detection at RaptorX.
}

\section{Patents \& Publications}
\cvitem{}{\textbf{Patents} (inventor): 20 applications spanning graph-based fraud detection and LLM/agent systems, with counsel: 6 filed (US), 4 published (India), 10 in draft. Published (India) App Nos.: 202541024623, 202541045354, 202441079562, 202541032797.}
\cvitem{}{\textbf{Publications} (first author; all under review):
\begin{itemize}
\item When the Tool Decides: LLM Agents Defer Blindly to GNN Tools (TMLR; arXiv:2606.14476)
\item LLM Features Can Hurt GNNs: Concatenation Interference on Homophilous Graph Benchmarks (TMLR; arXiv:2606.17579)
\item How Much Do Deep GNNs Actually Help? Decomposing Depth, Features, and Structure (NeurIPS 2026 E\&D)
\end{itemize}
}

\section{Technical Skills}
\cvitem{Agent / ML}{Agentic engineering, LLM APIs, function calling/tool use, guardrails, agent evaluation, PyTorch, PyG, GNNs, autoencoders, fraud-ring detection}
\cvitem{Data \& MLOps}{Spark / PySpark, Kafka, ClickHouse, Redis, Parquet, Docker, Kubernetes, ArgoCD, CI/CD, FastAPI / gRPC, MLflow}
\cvitem{Cloud}{AWS (S3 / EC2 / ECR), cloud GPU workflows, Linux, Grafana, Prometheus, Loki}

\section{Education}

\cventry{2018--2019}{University College London, London, UK.}{}{}{}{MSc in Data Science and Machine Learning. \\
Thesis: Graph Convolutional Networks for user behavior prediction (jointly with DiDi AI Labs). \\
Achieved top 3\% in group NLP research project among 300 students.
}

\cventry{2015--2018}{King's College London, London, UK.}{}{}{}{BSc in Computer Science (Artificial Intelligence).
}



\end{document}
